Evaluating `Graphical Perception' with CNNs

### 2018-03-31 PAPER/05_position_length_experiment.tex
Update section 5.

\noindent\textbf{Perceptual Performance.} In the original position-length experiment, Cleveland and McGill report that types 1-5 were post-ordered by their perceptual difficulty with type 1 being the easiest and type 5 the hardest. We report the average MLAE for each type across our networks (and total 56 runs per type) as follows: 
for type 1 $MLAE= 3.956 $ ($SD= 0.274 $),
for type 2 $MLAE= 3.952 $ ($SD= 0.441 $),
for type 3  $MLAE= 4.349 $ ($SD= 0.367 $),
for type 4 $MLAE= 3.668 $ ($SD= 0.256 $), and 
for type 5 $MLAE= 3.902 $ ($SD= 0.253 $). These distributions yield significance ($F_{4,25}=2.815, p<0.05$) but post hoc comparions show that really only type 3 and type 4 differ ($t_{10}=3.406, p<0.01$). This means that the networks do not prefer a certain type on average which leads us to \textbf{partially accept H3.1} and we do not replicate the same pattern as Cleveland and McGill in their human studies even though our networks' performance is clearly worse than their human baseline.
\\~\\
\noindent\textbf{`Multi' Network Performance.} In Cleveland and McGill's original position-length experiment, humans were asked to judge visualizations of types 1-5. In the bottom of Figure~\ref{fig:figure4_mlae} we average the human performances of types 1-5 to create a `multi' human. Similarly, when training our networks, we first limit each training to one stimuli. However, a `multi' network which learns types 1-5 simultaenously is closer to the human in the original user study. WHAT SHALL WE TEST HERE?

>>>>

\noindent\textbf{Perceptual Performance.} In the original position-length experiment, Cleveland and McGill report that types 1-5 were post-ordered by their perceptual difficulty with type 1 being the easiest and type 5 the hardest. We report the average MLAE for each type across our networks (and total 56 runs per type) as follows: 
for type 1 $MLAE= 3.956 $ ($SD= 0.274 $),
for type 2 $MLAE= 3.952 $ ($SD= 0.441 $),
for type 3  $MLAE= 4.349 $ ($SD= 0.367 $),
for type 4 $MLAE= 3.668 $ ($SD= 0.256 $), and 
for type 5 $MLAE= 3.902 $ ($SD= 0.253 $). These distributions yield significance ($F_{4,25}=2.815, p<0.05$) but post hoc comparions show that really only type 3 and type 4 differ ($t_{10}=3.406, p<0.01$). This means that the networks do not prefer a certain type on average which leads us to \textbf{partially accept H3.1} and we do not replicate the same pattern as Cleveland and McGill in their human studies even though our networks' performance is clearly worse than their human baseline.
\\~\\
\noindent\textbf{`Multi' Network Performance.} In Cleveland and McGill's original position-length experiment, humans were asked to judge visualizations of types 1-5. In the bottom of Figure~\ref{fig:figure4_mlae} we average the human performances of types 1-5 to create a `multi' human. Similarly, when training our networks, we first limit each training to one stimuli. However, a `multi' network which learns types 1-5 simultaenously is closer to the human in the original user study. For our `multi' experiment, we record an average error across all classifiers of $MLAE=4.358$ ($SD=0.327$). We then compare against the average errors for all types, as reported above for perceptual performance. We reach significant differences ($F_{5,30}=3.454,p<0.05$). Post hoc comparisons yield significant differences between the `multi' experiment and type 4 ($t_{10}=3.716, p<0.01$) and also to type 5 ($t_{10}=2.467, p<0.05$). Since our the average MLAE is worse than all of type 1--5, and the distributions observe significant differences, we acknowledge that the `multi' task is harder for the networks than learning single types of encodings. This might relate to us fixing all other parameters of the experiment such as the number of early stopping epochs and the size of training data, however, we \textbf{reject H3.2}.
